COVID-19 and Online Learning Tools

### 2021-12-28 Paper_online_Learning.tex
updated

Good psychosocial support is also vital to improve both students' and teachers' mental health and well-being during a pandemic. This is evident from the two sudden spikes in the search volume index graphs of the term `Psychosocial support' ( Figure \ref{fig:psychosocialSupport} ) which correspond well with the academic breaks in August in both years, 2020 and 2021, under `Education' category. This highlight the urgent need of attention and solutions towards these aspects. This type of an analysis based on secondary data is vital as these aspects can be easily overlooked due to the lack of connection and communication between students and educators during school closures.

@@

In this study we investigated whether the Google Trend search queries can be used as a proxy of the popularity and the public interest in different distance education solutions. This study is the first detailed analysis of web search behaviour related to distance learning solutions, both in quantitative and qualitative terms during COVID-19 pandemic. A few previous published studies \autocite{vaughan2014web,kansal2021google} have investigated Google trend search queries related to education, but only with a limited number of search terms or different focuses.

Our findings suggest that web search interest in distance education at the global level was strongly influenced by the COVID-19 pandemic. Google Trend search queries showed a strong cross correlation between COVID-19 related search terms and distance education related search terms. The high popularity and increasing public attention towards different distance learning solutions during COVID-19 pandemic was also investigated through a detailed Google Trend footprint analysis. The findings will help the educators to narrow down their search space and thereby select prominent options available in the market for different education purposes. According to \textcite{wallace2003online}, the learning tools can have a significant impact on how students engage in online learning. The finding will also helpful for developers to identify their competitors in the market. High cost involved with different distance learning solutions, lack of financial support/funding and lack of understanding about the existing distance learning solutions are some of the major issues the educational institutions face with the COVID-19 pandemic. Therefore, the findings of this study offer important insights to various stakeholders of education to make better decision with less time and effort.

Google Trends only captures the search behaviour of a sub population with Internet access, eventhough it is the most common worldwide search engine. Further, our study focused on global attention toward distance learning solutions during COVID-19 pandemic. Therefore, care should be given when generalizing these findings to different regions or different time periods, as different regions can have different market orientation and seasonal requirements. This can lead to variations in the search output and in turn the study findings for different regions and time frames. Further, Google Trends data were not available as absolute values and available only in the form of relative volume. Therfore the scores ranges from 0 to 100 do not allow the researchers to make meaningful comparisons across different education needs. Further investigation is needed at national and regional level to identify the specific measures that can be taken to ensure the quality of distance education at national and regional level.

@@

This work was carried out with the aid of a grant form UNESCO and the International Development Research Centre, Ottawa, Canada. The views expressed herein do not necessarily represent those of UNESCO, IDRC or its Board of Governors.

>>>>

Good psychosocial support is also vital to improving both students' and teachers' mental health and well-being during a pandemic. This is evident from the two sudden spikes in the search volume index graphs for the term `Psychosocial support' ( Figure \ref{fig:psychosocialSupport} ) which correspond well with the academic breaks in August in both years, 2020 and 2021, under `Education' category. This highlights the urgent need for attention and solutions to these aspects. This type of analysis based on secondary data is vital as these aspects can be easily overlooked due to the lack of connection and communication between students and educators during school closures.

@@

In this study, we investigated whether the Google Trend search queries can be used as a proxy of the popularity and public interest in different distance education solutions. This study is the first detailed analysis of web search behaviour related to distance learning solutions during the COVID-19 pandemic, both in quantitative and qualitative terms. A few previous published studies \autocite{vaughan2014web,kansal2021google} looked at Google trend search queries related to education, but only with a limited number of search terms or with different focuses.

Our findings suggest that web search interest in distance education at the global level was strongly influenced by the COVID-19 pandemic. Google Trend search queries showed a strong cross correlation between COVID-19 related search terms and distance education related search terms. The high popularity and increasing public attention towards different distance learning solutions during the COVID-19 pandemic was also investigated through a detailed Google Trend footprint analysis. The findings will help educators to narrow down their search space and thereby select prominent options available in the market for different educational purposes. According to \textcite{wallace2003online}, the learning tools can have a significant impact on how students engage in online learning. The finding will also be helpful for developers to identify their competitors in the market. The high costs involved with different distance learning solutions, lack of financial support/funding, and lack of understanding about the existing distance learning solutions are some of the major issues educational institutions face with the COVID-19 pandemic. Therefore, the findings of this study offer important insights to various stakeholders in education to make better decisions with less time and effort.

Google Trends only captures the search behaviour of a sub-population with Internet access, even though it is the most common worldwide search engine. Furthermore, our study focused on global attention toward distance learning solutions during the COVID-19 pandemic. Therefore, care should be given when generalizing these findings to different regions or different time periods, as different regions can have different market orientation and seasonal requirements. This can lead to variations in the search output and in turn the study findings for different regions and time frames. Furthermore, Google Trends data is not available as absolute values but only in the form of relative volume. Therefore, the scores range from 0 to 100, which does not allow the researchers to make meaningful comparisons across different education needs. Further investigation is needed at national and regional level to identify the specific measures that can be taken to ensure the quality of distance education at national and regional level.

@@

This work was carried out with the aid of a grant from UNESCO and the International Development Research Centre, Ottawa, Canada. The views expressed herein do not necessarily represent those of UNESCO, IDRC or its Board of Governors.

### 2021-12-28 main.Rmd
updated

In this study  we investigated whether the Google  Trend search queries can be used as a proxy of the popularity and the public interest in different distance education solutions. This study is the first detailed analysis of web search behaviour related to distance learning solutions, both in quantitative and qualitative terms during COVID-19 pandemic. A few previous published studies [@vaughan2014web; @kansal2021google] have investigated Google trend search queries related to education, but only with a limited number of search terms or different focuses.

Our findings suggest that web search interest in distance education at the global level was strongly influenced by the COVID-19 pandemic. Google Trend search queries showed a strong cross correlation between COVID-19 related search terms and distance education related search terms. The high popularity and increasing public attention towards different distance learning solutions during COVID-19 pandemic was also investigated through a detailed Google Trend footprint analysis. The findings will help the educators to narrow down their search space and thereby select prominent options available in the market for different education purposes. According to @wallace2003online, the learning tools can have a significant impact on how students engage in online learning.   The finding will also helpful for developers to identify their competitors in the market. High cost involved with different distance learning solutions, lack of financial support/funding and lack of understanding about the existing distance learning solutions are some of the major issues the educational institutions face with the COVID-19 pandemic. Therefore, the findings of this study offer important insights to  various stakeholders of education  to make better decision with less  time and effort.

Google Trends only captures the search behaviour of a sub population with Internet access, eventhough it  is the most common worldwide search engine. Further, our study focused on global attention toward distance learning solutions during COVID-19 pandemic. Therefore, care should be given when generalizing these findings to different regions or different time periods, as different regions can have different market orientation and seasonal requirements. This can lead to variations in the search output and in turn the study findings for different regions and time frames.  Further, Google Trends data were not available as absolute values and available only in the form of relative volume.  Therfore the scores ranges from 0 to 100 do not allow the researchers to make meaningful comparisons across different education needs. Further investigation is needed at national and regional level to identify the specific measures that can be taken to ensure the quality of distance education at national and regional level.

>>>>

In this study, we investigated whether the Google  Trend search queries can be used as a proxy of the popularity and public interest in different distance education solutions. This study is the first detailed analysis of web search behaviour related to distance learning solutions during the COVID-19 pandemic, both in quantitative and qualitative terms. A few previous published studies [@vaughan2014web; @kansal2021google] looked at Google trend search queries related to education, but only with a limited number of search terms or with different focuses.

Our findings suggest that web search interest in distance education at the global level was strongly influenced by the COVID-19 pandemic. Google Trend search queries showed a strong cross correlation between COVID-19 related search terms and distance education related search terms. The high popularity and increasing public attention towards different distance learning solutions during the COVID-19 pandemic was also investigated through a detailed Google Trend footprint analysis. The findings will help educators to narrow down their search space and thereby select prominent options available in the market for different educational purposes. According to @wallace2003online, the learning tools can have a significant impact on how students engage in online learning.   The finding will also be helpful for developers to identify their competitors in the market. The high costs involved with different distance learning solutions, lack of financial support/funding, and lack of understanding about the existing distance learning solutions are some of the major issues educational institutions face with the COVID-19 pandemic. Therefore, the findings of this study offer important insights to  various stakeholders in education  to make better decisions with less  time and effort.

Google Trends only captures the search behaviour of a sub-population with Internet access, even though it  is the most common worldwide search engine. Furthermore, our study focused on global attention toward distance learning solutions during the COVID-19 pandemic. Therefore, care should be given when generalizing these findings to different regions or different time periods, as different regions can have different market orientation and seasonal requirements. This can lead to variations in the search output and in turn the study findings for different regions and time frames.  Furthermore, Google Trends data is not available as absolute values but only in the form of relative volume.  Therefore, the scores range from 0 to 100, which does not allow the researchers to make meaningful comparisons across different education needs. Further investigation is needed at national and regional level to identify the specific measures that can be taken to ensure the quality of distance education at national and regional level.
